Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
fixing spelling and adding comment

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and convenors of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice.

>>>>

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g., F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}. As the publishers of journals and conveners of domain-specific conferences the authors note the potential importance of professional societies in effecting changes in community practice. \katznote{I can't quite understand what the prev sentence says}
